---
title: "Index Mini-Homework"
author: "Mislael A. Valentin Cortes"
date: "`r Sys.Date()`"
output:
  revealjs::revealjs_presentation:
    fig_height: 4
    highlight: haddock
    reveal_options:
      chalkboard:
        theme: chalkboard
        toggleChalkboardButton: yes
        toggleNotesButton: yes
      previewLinks: yes
      progress: yes
      slideNumber: yes
    reveal_plugins:
    - chalkboard
    - zoom
    self_contained: no
    theme: solarized
    transition: convex
  radix::radix_article:
    toc: true
    toc_depth: 2
  html_document:
    highlight: haddock
    number_sections: yes
    theme: default
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pagedown::html_paged: 
    highlight: haddock
    toc: yes
    number_sections: yes
    theme: default
  bookdown::gitbook:
    highlight: haddock
    css: styles.css
    config:
      download:
      - introduction-to-R.pdf
      - introduction-to-R.epub
  tint::tintPdf:
    highlight: haddock
    number_sections: yes
    toc: yes
  bookdown::epub_book: default  
  tint::tintHtml:
    highlight: haddock
    number_sections: yes
    toc: yes
  tufte::tufte_handout:
    fig_height: 2.5
    toc: yes
    number_sections: yes
    latex_engine: xelatex
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```


```{r, include=FALSE}
library(ggplot2)
library(ggthemes)
library(grid)
library(tidyr)
library(WDI)
library(googleVis)
library(haven)
library(readxl)

WorldBankDataDemo <- read_excel("C:\\Users\\valen\\Box Sync\\mislaelv\\homework\\WorldBankDataDemo.xlsx")

```


# Background

## World Bank Data Life Expectancy Exercise Part 1 


```{r}
ggplot(WorldBankDataDemo, aes(x=year, y=life_expectancy, color=life_expectancy))+geom_point()+scale_colour_gradientn(colours = rainbow(2))+theme_minimal()+labs(title = "Life expectancy by year", x="Year", y="Life Expectancy")
```

## World Bank Data Life Expectancy Exercise Part 1.2 

```{r}
ggplot(WorldBankDataDemo, aes(x=year, y=life_expectancy, fill=year))+stat_summary(fun.y = "mean", geom = "bar")+labs(title = "World Bank Data: Life Expectancy by Year", x="Year", y="Life Expectancy")+theme_minimal()
```



## World Bank Data Life Expectancy Exercise Part 2


ggplot(myReshapedData, aes(x=xaxis, y=yaxis))+geom_bar(stat = "identity")+theme_minimal()



## Washtenaw County Map

Washtenaw %>% ggplot(aes(fill=estimate))+geom_sf()+scale_fill_viridis_c()+theme_minimal()+labs(title = "Washtenaw County", subtitle = "Median Family Income", fill="Median Income")